---
name: Travis  
surname: Gerke, ScD
position: "epidemiologist • data scientist • statistician"
address: "H. Lee Moffitt Cancer Center & Research Institute, 12902 Magnolia Drive, Tampa, FL 33612"
phone: +1 706 346 4899
www: travisgerke.com
email: "travisgerke@gmail.com"
#twitter: travisgerke
googlescholar: mP-fw2gAAAAJ
github: tgerke
linkedin: travisgerke
headcolor: 00589A
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education
\emph{Summary:} I am jointly trained as a statistician and epidemiologist. I apply these skills as a data science leader to guide data collection strategies (epidemiology) that will enable optimal insights and robust decision-making from downstream consumption (statistical translation).

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Doctor of Science (ScD), Epidemiology", "2014", "Harvard School of Public Health", "Boston, MA",
  "Master of Arts (AM), Biostatistics", "2011", "Harvard University", "Cambridge, MA",
  "Bachelor of Science (BS), Statistics", "2009", "University of Florida", "Gainesville, FL"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

\vspace{-.7cm}
```{r}
tribble(
  ~ Degree, ~ Year,
  "Bachelor of Arts (BA), Mathematics", "2009"
) %>% 
  detailed_entries(Degree, Year)
```

# Experience and impact
\emph{Summary:} My career as a quantitative scientist spans not only the traditional principal investigator role, but also includes enterprise leadership in the data science domain. I have led or collaborated on 14 successful grant applications, many of which helped drive my 75+ peer-reviewed publications and 5 scientific software releases. At the enterprise level, I guide implementation of data science platforms that enable rapid and reproducible analytic insights.

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
    "Health Informatics Director", "2020--present", "H. Lee Moffitt Cancer Center & Research Institute", "Tampa, FL", "Create value for Moffitt data consumers as the agile product owner of cloud-based data marts (AWS/Snowflake) and associated informatics tools (RStudio/Python/Shiny) designed meet the clinical, research, and operational analytics needs of Moffitt’s faculty and administration") %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
    "", "", "", "", "Facilitate data workflows across multiple teams around the Center, and provide the foundation for predictive analytics and data sharing partnerships",
    "Scientific Director, Collaborative Data Services", "2018--present", "", "", "Provide scientific and technical leadership for Moffitt's research data provisioning hub. Key initiatives include: (i) transition a traditionally Excel-based data group to modern R frameworks with git versioning; (ii) enhance interfacing with biostatistics/bioinformatics end-users to deliver analytically-ready data"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-.5cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Assistant Member, Department of Cancer Epidemiology", "2016--2020", "", "", "Direct academic research lab with emphasis in: (i) developing modernized data science workflows for molecular epidemiology research; (ii) causal inference for decision science and real world evidence studies; (iii) reproducible data science frameworks"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-.5cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Assistant Professor, Department of Epidemiology", "2014--2016", "University of Florida", "Gainesville, FL", "Direct research lab with emphasis in: (i) machine learning in studies of gene expression; (ii) methods for high-dimensional data reduction",
    "Statistician I / Research Data Analyst, Department of Epidemiology", "2011--2014", "Harvard School of Public Health", "Boston, MA", "As lead statistician in an epidemiology lab, ensure appropriate application of statistical methods and provide accompanying mentorship of students/postdocs as needed; as research data analyst, assist with manuscript and grant development",
  "Research Data Analyst, Department of Biostatistics", "2012--2013", "Dana-Farber Cancer Institute", "Boston, MA", "Lead Python developer in a collaboration with the Google Earth team to estimate public health impacts of global glacier retreat",
  "Research Data Analyst, Rehabilitation Outcomes Research Center", "2008--2009", "Department of Veterans Affairs", "Gainesville, FL", "Perform SAS-based econometric health-care delivery analyses",  
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\newpage

# Advisory roles, mentorship, and outreach
\emph{Summary:} As a result of my deep appreciation for modernized data governance, scientific computing, and reproducible data science frameworks, I provide strategic input for a wide array of relevant organizational initiatives. Successful implementation of such initiatives requires understanding the needs and partnership/mentoring of data science end-users. As an active and visible member of the broader data science community, I enjoy sharing successes/challenges and learning from the experience of others.

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Selected Advisory Roles", " ", " ", " ", "Moffitt Research Data Analyst Task Force (Chair): The goal of this task force was to modernize the institution's research data analyst job ladder to align with data science job seekers, both with respect to search criteria and salary expectations"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  " ", " ", " ", " ", "Moffitt High Performance Computing Steering Committee (Member): This committee ensures that services and technology stack offered by the Moffitt compute cluster meet the evolving needs of research end-users"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  " ", " ", " ", " ", "Moffitt Health and Research Informatics (HRI) Governance Committee (Member): This committee provides guidance and decision-making for data warehouse-related activities, and aims to build trust in the institution’s high quality data assets by establishing shared understanding through data availability, quality, and usability"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  " ", " ", " ", " ", "Flatiron Health Academic Research Oversight Committee (Member): This committee provides guidance on how to best use Flatiron national data to advance academic research and identify opportunities for collaboration across sites"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  " ", " ", " ", " ", "Flatiron R Package Universe (Core Team Member): This team of developers contributes to R packages which facilitate best practices in feature engineering and analysis of Flatiron real-world data"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-.2cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Selected Mentorship and Teaching Roles", " ", " ", " ", "AACR Integrative Molecular Epidemiology Workshop (annual faculty member, 2017--2020): At this workshop delivered to postdocs/early career faculty, I teach sections on effective use of big data resources and predictive modeling/machine learning"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  " ", " ", " ", " ", "University of Florida (2015--2016): In addition to formally mentoring 8 graduate students on thesis/dissertation committees, I designed and taught graduate courses focused on (i) measurement and data capture in health outcomes research and (ii) introductory causal inference"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  " ", " ", " ", " ", "Harvard School of Public Health Summer Program in Epidemiology, Introduction to Biostatistics and Statistical Programming (2013): I designed and taught an 8 week course which focused on using the R language to implement common biostatistical methods"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-.2cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Selected Outreach Activities", " ", " ", " ", "Founding Organizer, Tampa Bay R Users Group: Founded in 2017, this data science group has grown to over 500 members, and meets monthly to discuss introductory topics through state of the art in R programming"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-1.1cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  " ", " ", " ", " ", "Executive Board Member, Florida Interdisciplinary Data Sciences Consortium (2019--present): Provides a forum to advance interdisciplinary data science expertise and training to students, the USF community, and the state; features a biweekly seminar series and short courses/workshops"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

# Technical experience
\emph{Summary:} My philosphy on appropriate technology tooling is to use that which most efficiently delivers interpretable value to key stakeholders. This stance guides my regular usage and enthusiam for R/RStudio solutions which feature a full statistical toolkit with deliverables commonly designed for the modern web browser. I also have experience in cloud and/or high-performance computing cluster environments, where key stakeholders may be other data scientists who place high value on efficiency at scale; in such settings, I have deployed Python, SAS, or SQL (often through R database interfaces) as appropriate. In all technical work, I emphasize that reproduciblity and readability for future users of code is of paramount importance, with git playing a vital role in this regard.

\begin{center}•\hspace{.5em} R/R Markdown/Shiny \hspace{.5em}•\hspace{.5em} Python \hspace{.5em}•\hspace{.5em} Snowflake \hspace{.5em}•\hspace{.5em} SQL \hspace{.5em}•\hspace{.5em} SAS \hspace{.5em}•\hspace{.5em} git/GitHub \hspace{.5em}•\hspace{.5em} \LaTeX \hspace{.5em}•\end{center}
 
<!--
```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```
-->

<!--
# Publications

```{r}
scholar::get_publications("mP-fw2gAAAAJ&") %>% 
  filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = dplyr::row_number()) %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("gerke.bib")

bibliography_entries("gerke.bib")
```
-->
