---
name: Travis  
surname: Gerke, ScD
position: "epidemiologist • data scientist • statistician"
address: "H. Lee Moffitt Cancer Center & Research Institute, 12902 Magnolia Drive, Tampa, FL 33612"
phone: +1 813 745 6448
www: travisgerke.com
email: "travis.gerke@moffitt.org"
#twitter: travisgerke
googlescholar: mP-fw2gAAAAJ
github: tgerke
linkedin: travisgerke
headcolor: 00589A
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education
\emph{Summary:} I am jointly trained as a statistician and epidemiologist. I apply these skills as a data science leader to guide data collection strategies (epidemiology) that will enable optimal insights and robust decision-making from downstream consumption (statistical translation).

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Doctor of Science (ScD), Epidemiology", "2014", "Harvard School of Public Health", "Boston, MA",
  "Master of Arts (AM), Biostatistics", "2011", "Harvard University", "Cambridge, MA",
  "Bachelor of Science (BS), Statistics", "2009", "University of Florida", "Gainesville, FL"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

\vspace{-.7cm}
```{r}
tribble(
  ~ Degree, ~ Year,
  "Bachelor of Arts (BA), Mathematics", "2009"
) %>% 
  detailed_entries(Degree, Year)
```

# Experience and impact
\emph{Summary:} My career as a quantitative scientist spans not only the traditional principal investigator role, but also includes administrative leadership in the data science domain. I have led or collaborated on 14 successful grant applications, many of which helped drive my 70+ peer-reviewed manuscripts published or under review. My team science efforts have resulted in over 60 scientific conference presentations, both nationally and internationally. I have also led or co-developed 5 scientific software releases.

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Assistant Member, Department of Cancer Epidemiology", "2016--present", "H. Lee Moffitt Cancer Center & Research Institute", "Tampa, FL", "Research faculty"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-.6cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Scientific Director, Collaborative Data Services", " ", " ", " ", "Lead scientific direction"
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

\vspace{-.5cm}
```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~Why,
  "Assistant Professor, Department of Epidemiology", "2014--2016", "University of Florida", "Gainesville, FL", "Research faculty",
    "Statistician I / Research Data Analyst, Department of Epidemiology", "2011--2014", "Harvard School of Public Health", "Boston, MA", "Grant prep and manuscript writing",
  "Research Data Analyst, Department of Biostatistics", "2012--2013", "Dana-Farber Cancer Institute", "Boston, MA", "Python-based collaboration with Google Earth team",
  "Research Data Analyst, Rehabilitation Outcomes Research Center", "2008--2009", "Department of Veterans Affairs", "Gainesville, FL", "SAS-based econometric health-care delivery analyses",  
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```


# Leadership, advisory roles, and outreach
\emph{Summary:} teaching activities

 * Thing 1
 * Thing 2
 * Thing 3
 
# Technical experience

 * Thing 1
 * Thing 2
 * Thing 3
 
<!--
```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```
-->

<!--
# Publications

```{r}
scholar::get_publications("mP-fw2gAAAAJ&") %>% 
  filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("gerke.bib")

bibliography_entries("gerke.bib")
```
-->
